---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geoloc

The goal of geoloc is to provide access to the geolocation API from modern web-browser, in order to get the location of the user in a Shiny app. 

> Note that this location will be provided only if the user agrees to share it.

As it relies on the browser HTML API, this won't work with the RStudio native viewer.

This package has been tested on Google Chrome 68.0.3440.106 and Firefox 61.0.2. 

## Installation

You can install the dev version of {geoloc} from Github with:

``` r
remotes::install_github("ColinFay/geoloc")
```

## How it works 

### Getting the data

The two functions (described below) launch a prompt that asks the user if he is willing to share his/her location. 

If the user agrees, the `lat` and `long` are sent back to shiny in `input$geoloc_lon` and `input$geoloc_lat`. 

The communication from the browser to Shiny may take some time (a matter of seconds, though). 

### Error

There are four cases where the location can fail. They are sent back to Shiny as:

+ `"NOT_SUPPORTED"`: location not supported in the browser
+ `"PERMISSION_DENIED"`: the user did not allowed to be located
+ `"POSITION_UNAVAILABLE"`: the user location is not available
+ `"TIMEOUT"`: the operation timed-out

## Onload or With a button

There are two ways to get the user location:

### At page load time

You can get the location of the user as soon as the app loads with `onload_geoloc`.

```{r eval = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(
  geoloc::onload_geoloc(),
  leafletOutput("lf")
)

server <- function(input, output) {
  output$lf <- renderLeaflet({
    req(input$geoloc_lon)
    req(input$geoloc_lat)
    leaflet() %>%
      addTiles() %>%
      setView(as.numeric(input$geoloc_lon), as.numeric(input$geoloc_lat), zoom = 17) %>%
      addMarkers(as.numeric(input$geoloc_lon), as.numeric(input$geoloc_lat), label = "You're here!")
  })
}

shinyApp(ui, server)

```

### With a button 

`button_geoloc` behaves a any `shiny::actionButton` (and takes the same parameters), except that it launches the geolocation service when it is clicked.

```{r eval = FALSE}
library(shiny)
library(leaflet)

ui <- fluidPage(
  h2("Where Am I?"),
  tags$p("Click the button to get your location"),
  geoloc::button_geoloc("id", "Get my Location"),
  tags$br(),
  leafletOutput("lf")
)

server <- function(input, output) {
  output$lf <- renderLeaflet({
    req(input$geoloc_lon)
    req(input$geoloc_lat)
    leaflet() %>%
      addTiles() %>%
      setView(as.numeric(input$geoloc_lon), as.numeric(input$geoloc_lat), zoom = 17) %>%
      addMarkers(as.numeric(input$geoloc_lon), as.numeric(input$geoloc_lat), label = "You're here!")
  })
}

shinyApp(ui, server)

```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
